Cultural Transmission Can Explain the Evolution of Cooperation

### 2020-08-08 ms/main.tex
Fix results 3

%%% Figure: coexistence map
\begin{figure}[htb]
\centering
\includegraphics[scale=1]{coexistence.pdf}
\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$. The line of $\hat{p}'=\hat{p}$ is in dashed black. The curve and dashed line intersect at the equilibrium $\hat{p}^*$. 
The blue curve is above the black dashed line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$. The blue curve is below the orange line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
}
\label{fig:coexistence}
\end{figure}

@@

\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
\begin{enumerate}
\item \emph{Fixation of cooperation}, 
if $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
if $T_A>T_B$ and $0<\beta_3$; or 
if $T_A<T_B$ and $\beta_1<\beta_3$.
\item \emph{Fixation of the defection}, 
if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
if $T_A>T_B$ and $\beta_1<\beta_3<0$; or 
if $T_A<T_B$ and $\beta_3<0$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$},
if $T_A < T_B$ and $0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_3<\beta_1$.

>>>>

%%% Figure: coexistence map
\begin{figure}[htb]
\centering
\includegraphics[scale=1]{coexistence.pdf}
\caption{\textbf{Stable coexistence between cooperation and defection.} The frequency of the cooperative phenotype $A$ among juveniles in the next generation $\hat{p}'$ is plotted in blue as a function of the frequency in the current generation $\hat{p}$ for $T_A<T_B$ and $\gamma_2<c<\gamma_1$. The line of $\hat{p}'=\hat{p}$ is in dashed black. The curve and dashed line intersect at the equilibrium $\hat{p}^*$. 
The blue curve is above the black dashed line$\hat{p}<\hat{p}^*$, so that the frequency increases towards $\hat{p}^*$. The blue curve is below the black dashed line when $\hat{p}>\hat{p}^*$, so that the frequency decreases towards $\hat{p}^*$.
}
\label{fig:coexistence}
\end{figure}

@@

\begin{result}[Vertical, oblique, and horizontal transmission of cooperation] \label{result:vert_obli_hori}
The cultural evolution of a cooperator phenotype will follow one of the following scenarios, depending on the horizontal transmission bias $T_A-T_B$ and the coefficients $\beta_1$ and $\beta_3$:
\begin{enumerate}
\item \emph{Fixation of cooperation}, 
if $T=T_A=T_B$ and $c < b\cdot \frac{\alpha T}{1-T}$; or
if $T_A>T_B$ and $0<\beta_3$; or 
if $T_A<T_B$ and $\beta_1<\beta_3$.
\item \emph{Fixation of the defection}, 
if $T=T_A=T_B$ and $c > b\cdot \frac{\alpha T}{1-T}$; or 
if $T_A>T_B$ and $\beta_3<\beta_1<0$; or 
if $T_A<T_B$ and $\beta_3<0$.
\item \emph{Coexistence of both phenotypes at $\hat{p}^*$},
if $T_A < T_B$ and $0<\beta_3<\beta_1$.
\item \emph{Fixation of either phenotype depending on initial frequency}, if $T_A>T_B$ and $\beta_1<\beta_3 < 0$.
